Corpus Stats

### 2019-03-26 notebooks/corpus_stats_and_plots.Rmd
code

zzz %>%
ggplot(aes(x=names_o, value, group=1)) +
 geom_line(aes(colour = language), size=0.05) +
 labs(title = "Analysis of R Corpus (R and C)", y = "Lines of Code in Package (Log10-scaled)") + guides(colour=F) + 
 theme( axis.text.x  = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(),
        axis.ticks.y = element_line(),  panel.grid.major.y = element_line(colour = "red")) + # ,
  scale_y_continuous(name="Lines of Code in Package", breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(10000, 1000, 100, 10, 0, 10, 100, 1000, 10000))

>>>>

zzz %>%
ggplot(aes(x=names_o, value, group=1)) +
 geom_line(aes(colour = language), size=0.008) +
 labs(title = "Analysis of R Corpus (R and C)", y = "Lines of Code in Package (Log10-scaled)") + guides(colour=F) + 
 theme( axis.text.x  = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(),
        axis.ticks.y = element_line(),  panel.grid.major.y = element_line(colour = "red")) + # ,
  scale_y_continuous(name="Lines of Code in Package", breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(10000, 1000, 100, 10, 0, 10, 100, 1000, 10000))
